### 2022-07-29 Papers/ICCC-2023/sections/design.tex
stuff

\subsection{Compiler interface} 
\label{compiler-interface}

\subsection{Backend}
\label{backend}

>>>>

In CTFE First, interpreter is the heart of the compiler.
It executes the Compiler-Interface which translates the intermidiate representation into the backend's assembly and serves as what is sometimes called the 'middle-end' of the compiler\cite{hsu2021llvm}.
To do it, it must be able to treat the program's intermidiate representation both as code and data.

\subsection{Compiler Interface} 
\label{compiler-interface}

Compiler Interface translates the program's intermidaite representation into the backend's assembly language.
This component is interpreted during compilation.
What stands out about CTFE First is that this part of the compiler can thus be written in the target language, during Stage 0 of the compiler bootstrapping process, as was the case for the C-=-1 compiler\cite{puntambekar:compiler_design, novillo2007gcc, grabski2022compilation}.

Compiler Interface is a regular code package that contains a function marked as the Compiler Interface Entry-point.
That procedure must accept a set of modules to be compiled and a Compilation Context that is used to generate the Backends assembly.
The module descriptors that are passed to the Compiler Interface are built by the frontend, as can be seen in figure \ref{CTFE-first-compiler-structure}.

After the Compiler Interface has finished generating backend assembly, the Compiler Backend is invoked to generate the binary executable.
\subsection{Backend}
\label{backend}

### 2022-07-29 Papers/ICCC-2023/sections/implementation.tex
stuff

Figure \ref{fig:interpreter_data_structures} contains a class diagram of most of the types used to represent values within C-=-1.

>>>>

Figure \ref{fig:interpreter_data_structures} contains a class diagram of most of the types used to represent values within C-=-1.
All of them derive from \lstinline{IRuntimeValue} and are managed via C++ smart pointers.
The interface of the base class allows the value to be converted to a human readable format, serialisation, deserialisation and copying.

The most prymitive types within the hierarchy are \lstinline{StringValue} and \lstinline{IntegerValue}.
They are simple wrappers for strings and integers.
Floating point numbers were not implemented as they were not nessecary for implementation of a basic compiler.

User-defined types are represented using \lstinline{ObjectValue}.
The contents of an objects is kept as a \lstinline{string} - \lstinline{IRuntimeValue} dictionary, with field names as keys and \lstinline{uniqe_ptr<IRuntimeValue>} as values.
C-=-1 object is therefore spread out in memory, even if the fields are directly contained within the class, without any indirection.

There are multiple types of reference within the C-=-1 interpreter.
The most basic pointer type is a reference to C-=-1 value.
